### 2015-06-04 doc/manual/mscviewer.tex
refactored ColorPicker 'letter' subcomponent, added 'about memory'

>>>>

\section{The Source View}
The source View is a tab in the bottom-right part of the GUI. This view shows the original log file that was 
parsed to create the sequence diagram model. Lines that contributed event information are highlighted in blue, 
while other lines are shown in black. Clicking on an event line selects the correspoding event, provided that the
owning entity was open in the sequence diagram area. Selecting an event in the sequence diagram causes the 
corresponding line in the Source View to be selected. Double-clicking on an event line in the Source View
causes the corresponding entity to be opened in the sequence diagram and the event selected.

\section{The Data View}
Events may have associated structured data. The data associated to the selected event is shown in the Data View,
which is located inside a tab in the bottomr-right part of the GUI.

\section{The Notes View}
In order to facilitate a debugging session the user can associate notes to events. An note associated with an
event is shown as a small yellow square on the event. Selecting the event and right-mouse-clicking the user can
checkmark the "Note Sticker" menu item to make the note visible as a sticker in the sequence diagram.
To create a note, the user selects the event and edit the note in the Notes View, which is situated in a tab
in the bottom-right part of the GUI.

is a tab in the bottom-right part of the GUI. This view shows the original log file that was 
parsed to create the sequence diagram model. Lines that contributed event information are highlighted in blue, 
while other lines are shown in black. Clicking on an event line selects the correspoding event, provided that the
owning entity was open in the sequence diagram area. Selecting an event in the sequence diagram causes the 
corresponding line in the Source View to be selected. Double-clicking on an event line in the Source View
causes the corresponding entity to be opened in the sequence diagram and the event selected.
